\normalfont{A bird's-eye view on the habitability of exoplanets via statistical learning techniques}

### 2020-09-23 Manuscript/Manuscript.tex
PUB

>>>>

\begin{table}[]
\caption{A selected features of the exoplanets dataset provided by PHL @ UPR Arecibo\cite{planet_dataset} accompanied by their measure unit }
\begin{tabular}{@{}lll@{}}
\toprule
Variable name                                                                & Abbreviation & Description/Comments                                                                                      \\ \midrule
Planet name                                                                  & P\_NAME      & \begin{tabular}[c]{@{}l@{}}The planet name according to \\ the international convention\end{tabular}      \\ \midrule
Planet Period                                                                & P\_P         & The planet period (days)                                                                                  \\ \midrule
Stellar temperature                                                          & S\_T         & \begin{tabular}[c]{@{}l@{}}The star effective temperature\\ (K)\end{tabular}                              \\ \midrule
Planet distance                                                              & P\_D         & \begin{tabular}[c]{@{}l@{}}Mean distance between the planet \\ and the host star (AU)\end{tabular}        \\ \midrule
Planet Periastron                                                            & P\_P         & \begin{tabular}[c]{@{}l@{}}The minimum distance between \\ the planet and the host star (AU)\end{tabular} \\ \midrule
Planet apastron                                                              & P\_A         & \begin{tabular}[c]{@{}l@{}}The maximum distance between \\ the planet and host star (AU)\end{tabular}     \\ \midrule
\begin{tabular}[c]{@{}l@{}}Planet effective \\ thermal distance\end{tabular} & P\_D\_E      & (AU)                                                                                                      \\ \midrule
\begin{tabular}[c]{@{}l@{}}Planet mean stellar\\ flux\end{tabular}           & P\_F         & (earth units)                                                                                             \\ \midrule
\begin{tabular}[c]{@{}l@{}}Planet equilibrium \\ temperature\end{tabular}    & P\_T\_E      & An albedo of 0.3 is considered (K)                                                                        \\ \midrule
Star radius estimated                                                        & S\_R\_E      & (solar units)                                                                                             \\ \midrule
Star luminosity                                                              & S\_L         & (solar units)                                                                                             \\ \midrule
Planet Habitability                                                          & P\_H         & 1 habitable, 0 else                                                                                       \\ \midrule
\begin{tabular}[c]{@{}l@{}}Estimated planet \\ radius\end{tabular}           & P\_R         & (earth units)                                                                                             \\ \midrule
\begin{tabular}[c]{@{}l@{}}Estimated planet\\ mass\end{tabular}              & P\_M         & (earth units)                                                                                             \\ \midrule
Star Spectral Type                                                           & S\_S\_T      & \begin{tabular}[c]{@{}l@{}}The star spectral type according\\ to the diagram in Fig. \ref{H_R_diagram} \end{tabular}         \\ \bottomrule
\end{tabular}
\end{table}

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Pic/S_T_T_explanation.png}
\caption{The Hertzsprung–Russell diagram (H-R): the phases that occurs during the lifetime of a star are placed on a plot that involves the surface temperature (and so the spectral type) vs the star luminosity.   Image taken from \cite{HR_diagram}}
\label{H_R_diagram}
\end{center}
\end{figure}
